---
title: "ver1"
author: "nightowl"
date: "September 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(dplyr)
library(tidyverse)
library(jsonlite)
library(magrittr)
```

## Load data

```{r load data, include=FALSE}
train <- read.csv("train.csv")
test <- read.csv("test.csv")
```

## COnvert JSON to columns (borrowed from kxx kernel)
```{r}


### 
flatten_json <- . %>% 
  str_c(., collapse = ",") %>%  #combine all rows into one big strings
  str_c("[", ., "]") %>%  #put open and close bracket
  jsonlite::fromJSON(.,flatten = T) #flatten the JSON list

parse <- . %>% 
  bind_cols(flatten_json(.$device)) %>%
  bind_cols(flatten_json(.$geoNetwork)) %>% 
  bind_cols(flatten_json(.$trafficSource)) %>% 
  bind_cols(flatten_json(.$totals)) %>% 
  select(-device, -geoNetwork, -trafficSource, -totals)


train <- parse(train)
test <- parse(test)

```

## Quick data count


```{r data check, echo=FALSE}

load("working_file.RData")

glimpse(train)
glimpse(test)


# different columns between train and test

setdiff(names(train),names(test)) #"campaignCode"       "transactionRevenue"

# remove campaignCode from train as it does not exist in test

train %<>% select(-one_of("campaignCode"))

# unique count of all columns and identify single value columns
col_remove <- train %>% summarise_all(n_distinct) %>% gather("key") %>% filter(value==1) %>% select(key)

# remove single value columns
train %<>% select(-one_of(col_remove[["key"]]))
test %<>% select(-one_of(col_remove[["key"]]))

train %>% summarise_all(n_distinct) %>% gather("key") %>%
ggplot(aes(x=reorder(key,desc(value)), y=value, label=value)) +
  geom_col()+
  theme_minimal()+
  geom_text()+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

# Channel grouping count
train %>% group_by(channelGrouping) %>% tally()
test %>% group_by(channelGrouping) %>% tally()

# social Engagement count
train %>% group_by(socialEngagementType) %>% tally()
test %>% group_by(socialEngagementType) %>% tally()

# visit number count
train %>% group_by(visitNumber) %>% tally()
test %>% group_by(visitNumber) %>% tally()

# NA count
train %>% group_by(visitNumber) %>% tally()
```
- channelGrouping: convert to factor.
- date: convert to date format
- device: convert json format to columns
- fullvisitorId: ok
- geoNetwork: convert json format to columns
- sessionId: ok
- socialEngagementType: single value. remove
- totals: convert json format to columns
- trafficSource: convert json format to columns
- visitID: conver to character
- visitNumber: ok
- visitStartTime: convert to date

```{r}
 
test %>% summarise_all(n_distinct) %>% gather("key") %>% filter(value==1)
  # ggplot(aes(x=reorder(key,desc(value)), y=value, label=value)) +
  # geom_col()+
  # theme_minimal()+
  # geom_text()+
  # theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

